Notes

### 2024-02-03 chapters/experiments.tex
Update reference
Minor change in naming

\paragraph{Logistic regression comparison algorithms.} All the variable selection and dimension reduction algorithms from above are also considered in this case, plus the following classification methods:
\begin{itemize}
  \item Log.\hspace{.3em} Standard multiple logistic regression with \(l^2\) regularization.
  \item LDA.\hspace{.3em} Linear discriminant analysis.
  \item QDA.\hspace{.3em} Quadratic discriminant analysis.
  \item RKVS.\hspace{.3em} RKHS-based variable selection method proposed in \citet{berrendero2018use}.
  \item APLS.\hspace{.3em} Functional PLS used as a dimension reduction method, as proposed in \citet{delaigle2012achieving} in combination with the nearest centroid (NC) algorithm.
  \item FLog.\hspace{.3em} Functional RKHS-based logistic regression algorithm proposed in \citet{berrendero2018functional}.
  \item FLDA.\hspace{.3em} Implementation of the functional version of linear discriminant analysis proposed in \citet{preda2007pls}.
  \item MDC.\hspace{.3em} Maximum depth classifier \citep[e.g.][]{ghosh2005maximum}.
  \item FKNN.\hspace{.3em} Functional K-nearest neighbors classifier with the \(L^2\)-distance.
  \item FNC.\hspace{.3em} Functional nearest centroid classifier with the \(L^2\)-distance.
\end{itemize}

@@

Lastly, the results for the non-GP case can be seen in Figure~\ref{fig:reg_emcee_nongp}, in which the regressors are realizations of a GBM. In this case we still get better results under the RKHS model, while the results under the \(L^2\)-model are slightly worse. However, as before, the difference is small (except for the \textit{emcee\_mean} methods).

@@

\begin{figure}[ht!]
  \centering
  \includegraphics[width=.65\textwidth]{reg_emcee_nongp}
  \caption{RMSE of predictors for simulated data with GBM regressors (lower is better).}\label{fig:reg_emcee_nongp}
\end{figure}

@@

Finally, Figure~\ref{fig:clf_emcee_nongp} shows that our classifiers perform better than most comparison algorithms when separating two homoscedastic Gaussian processes, but they struggle in the heteroscedastic case. Incidentally, this heteroscedastic case of two zero-mean Brownian motions has a special interest, since it can be shown that the Bayes error is zero in the limit of dense monitoring (i.e. with an arbitrarily fine measurement grid), a manifestation of the ``near-perfect'' classification phenomenon analyzed for example in \citet{torrecilla2020optimal}. Our results are in line with the empirical studies of this article, where the authors conclude that even though the asymptotic theoretical error is zero, most classification methods are suboptimal in practice (possibly due to the high collinearity of the data), with the notable exception of PCA+QDA.

@@

\begin{figure}[htbp!]
  \centering
  \includegraphics[width=.65\textwidth]{clf_emcee_nongp}
  \caption{Accuracy of classifiers for simulated data coming from two different GP's, labeled according to their origin (higher is better).}\label{fig:clf_emcee_nongp}
\end{figure}

>>>>

\paragraph{Logistic regression comparison algorithms.} All the variable selection and dimension reduction algorithms from above are also considered in this case, plus the following classification methods:
\begin{itemize}
  \item Log.\hspace{.3em} Standard multiple logistic regression with \(l^2\) regularization.
  \item LDA.\hspace{.3em} Linear discriminant analysis.
  \item QDA.\hspace{.3em} Quadratic discriminant analysis.
  \item RKVS.\hspace{.3em} RKHS-based variable selection method proposed in \citet{berrendero2018use}.
  \item APLS.\hspace{.3em} Functional PLS used as a dimension reduction method, as proposed in \citet{delaigle2012achieving} in combination with the nearest centroid (NC) algorithm.
  \item FLog.\hspace{.3em} Functional RKHS-based logistic regression algorithm proposed in \citet{berrendero2023functional}.
  \item FLDA.\hspace{.3em} Implementation of the functional version of linear discriminant analysis proposed in \citet{preda2007pls}.
  \item MDC.\hspace{.3em} Maximum depth classifier \citep[e.g.][]{ghosh2005maximum}.
  \item FKNN.\hspace{.3em} Functional K-nearest neighbors classifier with the \(L^2\)-distance.
  \item FNC.\hspace{.3em} Functional nearest centroid classifier with the \(L^2\)-distance.
\end{itemize}

@@

Lastly, the results for the non-GP case can be seen in Figure~\ref{fig:reg_emcee_non_gp}, in which the regressors are realizations of a GBM. In this case we still get better results under the RKHS model, while the results under the \(L^2\)-model are slightly worse. However, as before, the difference is small (except for the \textit{emcee\_mean} methods).

@@

\begin{figure}[ht!]
  \centering
  \includegraphics[width=.65\textwidth]{reg_emcee_non_gp}
  \caption{RMSE of predictors for simulated data with GBM regressors (lower is better).}\label{fig:reg_emcee_non_gp}
\end{figure}

@@

Finally, Figure~\ref{fig:clf_emcee_non_gp} shows that our classifiers perform better than most comparison algorithms when separating two homoscedastic Gaussian processes, but they struggle in the heteroscedastic case. Incidentally, this heteroscedastic case of two zero-mean Brownian motions has a special interest, since it can be shown that the Bayes error is zero in the limit of dense monitoring (i.e. with an arbitrarily fine measurement grid), a manifestation of the ``near-perfect'' classification phenomenon analyzed for example in \citet{torrecilla2020optimal}. Our results are in line with the empirical studies of this article, where the authors conclude that even though the asymptotic theoretical error is zero, most classification methods are suboptimal in practice (possibly due to the high collinearity of the data), with the notable exception of PCA+QDA.

@@

\begin{figure}[htbp!]
  \centering
  \includegraphics[width=.65\textwidth]{clf_emcee_non_gp}
  \caption{Accuracy of classifiers for simulated data coming from two different GP's, labeled according to their origin (higher is better).}\label{fig:clf_emcee_non_gp}
\end{figure}
